Dual-Mode PSK Transceiver on SDR With FPGA

### 2024-01-08 latex/paper.tex
Working on Paper
Add waves.

@@

@@

@@

      \begin{figure}[htbp]
        \centering
        \input{tikz/sim/sync_BPSK}
        \caption{Carrier synchronization for BPSK}
      \end{figure}

@@

    The hardware resources consumption on Zynq-7020 with the default synthesis and implementation strategy is shown in Table~\ref{tab:resource}.
    Therefore, the design itself is area-efficient, and can be readily incorporated into a larger system.
    \begin{table}[htbp]
      \caption{Hardware Resources Consumption on Zynq-7020}
      \label{tab:resource}
    \end{table}

@@

    \begin{figure*}
      \setlength{\tabcolsep}{2pt}
      \newcommand\Modulation{BPSK}%
      \newcommand\IsBPSK1%
      \subfloat[A \Modulation{} packet.]{%
        \sffamily\notsotiny
        \begin{tabularx}{\linewidth}{@{}lX@{}}
          DAC\_vld & \input{tikz/ila/DAC_vld} \\
          DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
          DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
          ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
          ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
          I\_16M[15:0] & \input{tikz/ila/I_16M} \\
          Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
          I\_1M[15:0] & \input{tikz/ila/I_1M} \\
          Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
        \end{tabularx}%
      }\\
      \renewcommand\Modulation{QPSK}%
      \renewcommand\IsBPSK0%
      \subfloat[A \Modulation{} packet.]{%
        \sffamily\notsotiny
        \begin{tabularx}{\linewidth}{@{}lX@{}}
          DAC\_vld & \input{tikz/ila/DAC_vld} \\
          DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
          DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
          ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
          ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
          I\_16M[15:0] & \input{tikz/ila/I_16M} \\
          Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
          I\_1M[15:0] & \input{tikz/ila/I_1M} \\
          Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
        \end{tabularx}%
      }
      \caption{System ILA results.}
    \end{figure*}

>>>>

      The packetizer FSM has 5 states: IDLE, HDR, PLD, LAST and WAIT.
      The IDLE state is used to wait for the packet start.
      It transits to the HDR state when the valid and ready signals are both high,
      i.e., the packet starts transmitting.
      The HDR state is used to transmit the header (including TRN and HDR)%
      \footnote{For the packetizer and the depactizer, we do not distinguish TRN and HDR for simplicity,
      and they are called the header in contrast to the payload.}%
      , as discussed in Section~\ref{subsec:frame_structure}.
      It then transmits to the PLD state to transmit the payload stored in the FIFO.
      Notably, the FIFO depth should not be smaller than the header length (i.e. $32$).

@@

    In all Verilog simulation,
    random is added to the Rx ADC, to better simulate the real-world scenario.

@@

      The simulation results of the Costas loop are shown in Fig.~\ref{fig:sync_BPSK}.
      In the BPSK mode, the Costas loop can successfully handle the CFO smaller than \qty{7.81}{kHz}.
      It can be verified by the fact that the feedback saturates around a constant (corresponding to the CFO value),
      which .
      In the QPSK mode, the value is \qty{1.96}{kHz}.
      The convergence is relatively fast.
      \begin{figure}[htbp]
        \centering
        \input{tikz/sim/sync_BPSK}
        \caption{Carrier synchronization for BPSK. The feedback value after the loop filter v.s.\ time, with different CFO.}
        \label{fig:sync_BPSK}
      \end{figure}

@@

@@

    The hardware resources consumption on Zynq-7020 with the default synthesis and implementation strategy is shown in Table~\ref{tab:resource}.
    Therefore, the design itself is area-efficient, and can be readily incorporated into a larger system.
    \begin{table}[htbp]
      \caption{Hardware Resources Consumption on Zynq-7020}
      \label{tab:resource}
      \renewcommand{\arraystretch}{1.2}
      \rowcolors{1}{white}{gray!15}
      \begin{tabularx}{\linewidth}{YYYY}
        \toprule\tabvertspace
        \textbf{Resource} & \textbf{Utilization} & \textbf{Available} & \textbf{Util.\ Rate} \\
        \tabvertspace\midrule
        LUT & 7,248 & 53,200 & \hphantom{0}8.04\% \\
        LUTRAM & 1,121 & 17,400 & \hphantom{0}6.44\% \\
        FF & 8,144 & 106,400\hphantom{0} & \hphantom{0}7.65\% \\
        BRAM & \hphantom{0,0}27 & \hphantom{00,}140 & 19.29\% \\
        DSP & \hphantom{0,0}51 & \hphantom{00,}220 & 23.18\% \\
        IO & \hphantom{0,0}33 & \hphantom{00,}200 & 16.50\% \\
        BUFG & \hphantom{0,0}10 & \hphantom{00,0}32 & 31.25\% \\
        MMCM & \hphantom{0,00}2 & \hphantom{00,00}4 & 50.00\% \\
        \bottomrule
      \end{tabularx}
    \end{table}

@@

    \begin{figure*}
      \setlength{\tabcolsep}{2pt}
      \newcommand\Modulation{BPSK}%
      \newcommand\IsBPSK1%
      \subfloat[A \Modulation{} packet.]{%
        \sffamily\notsotiny
        \begin{tabularx}{\linewidth}{@{}lX@{}}
          DAC\_vld & \input{tikz/ila/DAC_vld} \\
          DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
          DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
          ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
          ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
          I\_16M[15:0] & \input{tikz/ila/I_16M} \\
          Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
          I\_1M[15:0] & \input{tikz/ila/I_1M} \\
          Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
          DAC\_bits[1] & \input{tikz/ila/DAC_bits_1} \\
          DAC\_bits[0] & \input{tikz/ila/DAC_bits_0} \\
          Rx\_data\_tdata[1] & \input{tikz/ila/Rx_data_tdata_1} \\
          Rx\_data\_tdata[0] & \input{tikz/ila/Rx_data_tdata_0} \\
          Rx\_data\_tvalid & \input{tikz/ila/Rx_data_tvalid} \\
          Rx\_data\_tuser & \input{tikz/ila/Rx_data_tuser} \\
          Tx\_1bit & \input{tikz/ila/Tx_1bit} \\
          Tx\_vld & \input{tikz/ila/Tx_vld} \\
          Rx\_1bit & \input{tikz/ila/Rx_1bit} \\
          Rx\_vld & \input{tikz/ila/Rx_vld} \\
        \end{tabularx}%
      }\\
      \renewcommand\Modulation{QPSK}%
      \renewcommand\IsBPSK0%
      \subfloat[A \Modulation{} packet.]{%
        \sffamily\notsotiny
        \begin{tabularx}{\linewidth}{@{}lX@{}}
          DAC\_vld & \input{tikz/ila/DAC_vld} \\
          DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
          DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
          ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
          ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
          I\_16M[15:0] & \input{tikz/ila/I_16M} \\
          Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
          I\_1M[15:0] & \input{tikz/ila/I_1M} \\
          Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
          DAC\_bits[1] & \input{tikz/ila/DAC_bits_1} \\
          DAC\_bits[0] & \input{tikz/ila/DAC_bits_0} \\
          Rx\_data\_tdata[1] & \input{tikz/ila/Rx_data_tdata_1} \\
          Rx\_data\_tdata[0] & \input{tikz/ila/Rx_data_tdata_0} \\
          Rx\_data\_tvalid & \input{tikz/ila/Rx_data_tvalid} \\
          Rx\_data\_tuser & \input{tikz/ila/Rx_data_tuser} \\
          Tx\_1bit & \input{tikz/ila/Tx_1bit} \\
          Tx\_vld & \input{tikz/ila/Tx_vld} \\
          Rx\_1bit & \input{tikz/ila/Rx_1bit} \\
          Rx\_vld & \input{tikz/ila/Rx_vld} \\
        \end{tabularx}%
      }
      \caption{System ILA results.}
    \end{figure*}
